Run AwAI: StarCraftII Adversary Avoidance Using Neural Networks and Genetic Algorithms

### 2018-06-04 doc/run_awai.tex
short conclusion

\section{Conclusion}
Different selection types?

>>>>

\section{Conclusion}
Based on the convergence we got during our trials, our method of training a
neural network to run away is a feasable approach to the problem. Although we
arguably did not achieve ``optimal'' results, given more time we are confident
that we could significantly improve the convergence of our algorithm.

We have demonstrated that evolving neural networks using a genetic algorithm is
a good approach to teaching agents to accomplish goals in countinuous or near
countinuous state spaces.
